Report

### 2015-09-08 Report Aug 5 2015/Report Aug 2015.tex

\begin{document}
%\begin{spacing}{8}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Report}

@@

\subsection{Risk Functional}

@@

minimize\quad \lambda||w||^{2}+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x})),

@@

minimize \quad \frac{1}{2}||w||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),

@@

\subsection{Lagrange Duality}

@@

The sufficient and necessary condition that $f(\mathbf{w}^{*})$ is the global minimum of (\ref{primal objective function}) is called Karush Kuhn Tucker conditions, which can be written as 
\begin{IEEEeqnarray}[\relax]{l}
\frac{\partial \Theta}{\partial \mathbf{w}}=w-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\\\label{partial1}
\frac{\partial \Theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0\\\label{partial2}
\frac{\partial \Theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0\\\label{parial3}
\frac{\partial \Theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\
\label{partial4}
\left\{\begin{array}{cc}
\alpha, \hat{\alpha}\geq 0\\
\alpha(y-\mathbf{w}^{T}\Phi(\mathbf{x})-b-\epsilon-\xi)=0\\
\hat{\alpha}(\mathbf{w}^{T}\Phi(\mathbf{x})+b-y-\epsilon-\hat{\xi})=0
\end{array}\right. \label{KKT complimentary}
\end{IEEEeqnarray}

The conditions in (\ref{KKT complimentary}) is called KKT complimentary condition. Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}) and for sake of brevity, we make $C_{i}$ uniform to all data samples, we have the dual form ：
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\theta(\alpha, \hat{\alpha}) =\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{l}[(R(\xi_{i})-\xi_{i}R^{'}(\xi_{i}))\\
\nonumber
+(R(\hat{\xi}_{i})-\hat{\xi}_{i}R^{'}(\hat{\xi}_{i}))]
+\sum_{i=1}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
\nonumber
-\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i}),\\
s.t.\left\{\begin{array}{l}
\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})=0\\
0<\alpha<C\tilde{R}^{'}(\alpha)\\
0<\hat{\alpha}<C\tilde{R}^{'}(\hat{\alpha})\\
\end{array}\right.
\label{dual objective function1}
\end{IEEEeqnarray}
Obviously $\theta(\alpha,\hat{\alpha})\leq \Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})$, Because 
\begin{equation}
\Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})=f(\mathbf{w})+\sum_{i}(\alpha_{i} g_{i}(\mathbf{w})+\hat{\alpha}_{i}\hat{g}_{i}(\mathbf{w}))+\sum_{i}(\eta_{i} l_{i}(\mathbf{w})+\hat{\eta}_{i}\hat{l}_{i}(\mathbf{w})),\label{Theta function}
\end{equation} 
where $g_{i}(\mathbf{w})$, $\hat{g_{i}(\mathbf{w})}$, $l_{i}(\mathbf{w})$, $\hat{l}_{i}(\mathbf{w})$ denote inequality constraints.
\begin{IEEEeqnarray}[\relax]{l}
g_{i}(\mathbf{w})=\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}\leq 0\\
\hat{g}_{i}(\mathbf{w})=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon-\hat{\xi}_{i}\leq 0\\
l_{i}(\mathbf{w})=-\xi_{i}\leq 0\\
\hat{l}_{i}(\mathbf{w})=-\hat{\xi}_{i}\leq 0\\
\end{IEEEeqnarray}
Hence $\Theta\leq f(\mathbf{w})$, we have $\theta\leq \Theta\leq f(\mathbf{w})$, therefore the upper bound of $\theta$ is determined by the original objective function $f(\mathbf{w})$. when $\theta=f(\mathbf{w})$,  according to (\ref{Theta function}), the linear combination term of inequality constraints equal to zero, that is, KKT complimentary conditions in (\ref{KKT complimentary}) satisfied. hence the global optimal point is found for both $\theta$ and $f(\mathbf{w})$ if and only if the equality holds. Therefore duality gap is defined as $G=f(\mathbf{w})-\theta$, which can be used as an evaluation for the closeness of one solution to the global optimal.

In conclusion, the dual objective function can be written as 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize\quad \Theta =-\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+\sum_{i=i}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
\nonumber
+C\sum_{i=1}^{l}[\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi_{i}})]\\
=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon)^{T}\mathbf{a}+(-\mathbf{y}-\epsilon)^{T}\mathbf{\hat{a}}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
\label{dual optimization function2}
\end{IEEEeqnarray}
where $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{l}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{l}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{l}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{l}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0,  $\tilde{R}(\xi)=R(\xi)-\xi R^{'}(\xi)\in \mathbb{R}^{l}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes data kernel matrix. We define the following $2l$ vectors 
$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2l}$, 
\begin{IEEEeqnarray}[\relax]{l}
\mathbf{v}_{i}=\left\{\begin{array}{ll}
1\quad i=1,\ldots, l\\
-1\quad i=l+1,\ldots, 2l\\ 
\end{array}\right.
\end{IEEEeqnarray}
(\ref{dual optimization function2}) can also be reformulate as 
\newcommand{\mysmallarraydecl}{\renewcommand{%
\IEEEeqnarraymathstyle}{\scriptscriptstyle}%
\renewcommand{\IEEEeqnarraytextstyle}{\scriptsize}%
\renewcommand{\baselinestretch}{1.1}%
\settowidth{\normalbaselineskip}{\scriptsize
\hspace{\baselinestretch\baselineskip}}%
\setlength{\baselineskip}{\normalbaselineskip}%
\setlength{\jot}{0.25\normalbaselineskip}%
\setlength{\arraycolsep}{2pt}}
\begin{equation}
maximize\quad \Theta=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\mathbf{K}& -\mathbf{K}\\
-\mathbf{K}& \mathbf{K}
\end{IEEEeqnarraybox*}\right]
\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
\label{vectorize dual optimization function}
\end{equation}

@@

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\
+i(\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}-\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{j}\mathbf{h}^{H}_{i})
\label{complex duality regularization1}
\end{IEEEeqnarray}
Because $\mathbf{K}$ is Hermitian, thus $\mathbf{K}_{ij}=\mathbf{K}^{*}_{ji}$, if we have $r_{i}$ and $r_{j}$ $\in \mathbb{R}$, 
\begin{equation}
\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij}=-\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ji}=-\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij},
\end{equation}
Therefore
\begin{equation}
\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij}=0,
\label{conjugate1}
\end{equation}
Based on (\ref{conjugate1}), (\ref{complex duality regularization1}) can be changed to
\begin{equation}
||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{K}^{r}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{K}^{r}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta-\hat{\beta}_{i})\mathbf{K}^{i}_{ij}.
\label{complex duality regularization2}
\end{equation}
Apply (\ref{complex lagrange duality2}), (\ref{complex duality regression function}), (\ref{conjugate1}) and (\ref{complex duality regularization2}) to (\ref{complex lagrange duality1}), the final form of Lagrange duality can be obtained
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize\quad \Theta=-\frac{1}{2}[\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}+\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}]\\
\nonumber
-\sum_{i}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta+\hat{\beta}_{i})\epsilon+[\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})]\\
\nonumber
+C\sum_{i}^{N_{r}}(\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i}))\\ 
\left\{\begin{array}{ll}
0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
\xi^{r}(\hat{\xi}^{r})\geq 0\\
\xi^{i}(\hat{\xi}^{i})\geq 0\\
\end{array}\right.
\label{final complex lagrange duality}
\end{IEEEeqnarray}
which can be divided into 2 independent regression task,

@@

Fig.\ref{figure3} demonstrates the relation between the number of users ($N_{t}$) and $E[\ln(\phi_{om})]_{t}$ under cases of different numbers of antennas at base station ($N_{r}$). From Fig.\ref{figure3}, we can see, on the one hand, with $N_{r}$ fixed, $E[\ln(\phi_{om})]$ decreases while $N_{t}$ increases, however the gradient of each curve becomes more and more gentle. On the other hand, when $N_{r}$ becomes larger $E[\ln(\phi_{om})]$ becomes more insensitive to variation of $N_{t}$.
\section{Stopping Criteria}\label{stopping criteria}
As we have explained in section \ref{Introduce epsilon SVR}, the upper bound of Lagrangian dual objective function is determined by primal objective function further more the Lagrangian dual objective function equals to original objective function only when the optimal is found. Therefore, the gap between primal problem and dual problem is used to evaluate how is close is the current solution to global minimum. In our scenario, feasibility gap is employed as stopping criteria because of low computational cost and reliable performance.

  Based on the dual objective function in (\ref{final complex lagrange duality}) and the primal objective function in (\ref{complex objective function1}), based on the proposition of Lagrangian theorem

@@

 -\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})+Im(\mathbf{y}^{T})(\beta-\hat{\beta})-\epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})\\
+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi_{i}^{r})+\tilde{R}(\hat{\xi}_{i}^{r})+\tilde{R}(\xi_{i}^{i})+\tilde{R}(\hat{\xi}_{i}^{i})] \leq \frac{1}{2}||\mathbf{W}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})+R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})]
\label{duality gap1}

@@

 where $\mathbf{W}=\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}-i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{j}$. The duality gap can be obtained by 

@@

 -\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})+Im(\mathbf{y}^{T})(\beta-\hat{\beta})-\epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi_{i}^{r})+\tilde{R}(\hat{\xi}_{i}^{r})\\

>>>>

\begin{document}
\begin{spacing}{2}
%\doublespacing
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Report}

@@

\subsection{Risk Functional}\label{risk functional}

@@

minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x})),

@@

minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),

@@

\subsection{Lagrange Duality}\label{section lagrange duality}

@@

The sufficient and necessary condition that $f(\mathbf{w}^{*})$ is the global minimum of (\ref{primal objective function}) is called Karush-Kuhn-Tucker (KKT) conditions, which can be written as 
\begin{IEEEeqnarray}[\relax]{l}
\frac{\partial \Theta}{\partial \mathbf{w}}=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\\label{partial1}
\frac{\partial \Theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0\\\label{partial2}
\frac{\partial \Theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0\\\label{parial3}
\frac{\partial \Theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\label{partial4}
\nonumber
\end{IEEEeqnarray}
\begin{IEEEeqnarray}[\relax]{l}
\left\{\begin{array}{cc}
\alpha, \hat{\alpha}\geq 0\\
\alpha(y-\mathbf{w}^{T}\Phi(\mathbf{x})-b-\epsilon-\xi)=0\\
\hat{\alpha}(\mathbf{w}^{T}\Phi(\mathbf{x})+b-y-\epsilon-\hat{\xi})=0
\end{array}\right. 
\label{KKT complimentary}
\end{IEEEeqnarray}

The conditions in (\ref{KKT complimentary}) is called KKT complimentary condition. Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality1}) and for sake of brevity, we make $C_{i}$ uniform to all data samples, we have the dual form of objective function ：
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\theta(\alpha, \hat{\alpha}) =\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{l}[(R(\xi_{i})-\xi_{i}R^{'}(\xi_{i}))\\
\nonumber
+(R(\hat{\xi}_{i})-\hat{\xi}_{i}R^{'}(\hat{\xi}_{i}))]
+\sum_{i=1}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
\nonumber
-\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i}),\\
s.t.\left\{\begin{array}{l}
\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})=0\\
0<\alpha<C\tilde{R}^{'}(\alpha)\\
0<\hat{\alpha}<C\tilde{R}^{'}(\hat{\alpha})\\
\end{array}\right.
\label{dual objective function1}
\end{IEEEeqnarray}
Obviously $\theta(\alpha,\hat{\alpha})\leq \Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})$, notice now (\ref{partial1})-(\ref{partial4})are satisfied, therefore, KKT complimentary condition (\ref{KKT complimentary}) is the only requirement to find global optimal point of original optimization problem. Because 
\begin{equation}
\Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})=f(\mathbf{w})+\sum_{i}(\alpha_{i} g_{i}(\mathbf{w})+\hat{\alpha}_{i}\hat{g}_{i}(\mathbf{w}))+\sum_{i}(\eta_{i} l_{i}(\mathbf{w})+\hat{\eta}_{i}\hat{l}_{i}(\mathbf{w})),\label{Theta function}
\end{equation} 
where $g_{i}(\mathbf{w})$, $\hat{g_{i}(\mathbf{w})}$, $l_{i}(\mathbf{w})$, $\hat{l}_{i}(\mathbf{w})$ denote inequality constraints.
\begin{IEEEeqnarray}[\relax]{l}
g_{i}(\mathbf{w})=\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}\leq 0\\
\hat{g}_{i}(\mathbf{w})=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon-\hat{\xi}_{i}\leq 0\\
l_{i}(\mathbf{w})=-\xi_{i}\leq 0\\
\hat{l}_{i}(\mathbf{w})=-\hat{\xi}_{i}\leq 0\\
\nonumber
\end{IEEEeqnarray}
Hence $\Theta\leq f(\mathbf{w})$, we have $\theta\leq \Theta\leq f(\mathbf{w})$, therefore the upper bound of $\theta$ is determined by the original objective function $f(\mathbf{w})$. when $\theta=f(\mathbf{w})$,  according to (\ref{Theta function}), the linear combination term of inequality constraints equal to zero, that is, KKT complimentary conditions in (\ref{KKT complimentary}) satisfied. hence the global optimal point is found for both $\theta$ and $f(\mathbf{w})$ if and only if the equality holds. Therefore duality gap is defined as $G=f(\mathbf{w})-\theta$, which can be used as an evaluation for the closeness of one solution to the global optimal.

In conclusion, the dual objective function can be written as 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize\quad \theta =-\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+\sum_{i=i}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
\nonumber
+C\sum_{i=1}^{l}[\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi_{i}})]\\
=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon)^{T}\mathbf{a}+(-\mathbf{y}-\epsilon)^{T}\mathbf{\hat{a}}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
\label{dual optimization function2}
\end{IEEEeqnarray}
where $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{l}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{l}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{l}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{l}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0,  $\tilde{R}(\xi)=R(\xi)-\xi R^{'}(\xi)\in \mathbb{R}^{l}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes data kernel matrix. We define the following $2l$ vectors 
$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2l}$, 
\begin{IEEEeqnarray}[\relax]{l}
\mathbf{v}_{i}=\left\{\begin{array}{ll}
1\quad i=1,\ldots, l\\
-1\quad i=l+1,\ldots, 2l\\ 
\end{array}\right.
\end{IEEEeqnarray}
(\ref{dual optimization function2}) can also be reformulate as 
\newcommand{\mysmallarraydecl}{\renewcommand{%
\IEEEeqnarraymathstyle}{\scriptscriptstyle}%
\renewcommand{\IEEEeqnarraytextstyle}{\scriptsize}%
\renewcommand{\baselinestretch}{1.1}%
\settowidth{\normalbaselineskip}{\scriptsize
\hspace{\baselinestretch\baselineskip}}%
\setlength{\baselineskip}{\normalbaselineskip}%
\setlength{\jot}{0.25\normalbaselineskip}%
\setlength{\arraycolsep}{2pt}}
\begin{equation}
maximize\quad \Theta=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\mathbf{K}& -\mathbf{K}\\
-\mathbf{K}& \mathbf{K}
\end{IEEEeqnarraybox*}\right]
\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
\label{vectorize dual optimization function}
\end{equation}

@@

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\
+i(\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}-\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{j}\mathbf{h}^{H}_{i})
\label{complex duality regularization1}
\end{IEEEeqnarray}
Because $\mathbf{K}$ is Hermitian, thus $\mathbf{K}_{ij}=\mathbf{K}^{*}_{ji}$, if we have $r_{i}$ and $r_{j}$ $\in \mathbb{R}$, 
\begin{equation}
\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij}=-\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ji}=-\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij},
\end{equation}
Therefore
\begin{equation}
\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij}=0,
\label{conjugate1}
\end{equation}
Based on (\ref{conjugate1}), (\ref{complex duality regularization1}) can be changed to
\begin{equation}
||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{K}^{r}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{K}^{r}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}.
\label{complex duality regularization2}
\end{equation}
Apply (\ref{complex lagrange duality2}), (\ref{complex duality regression function}), (\ref{conjugate1}) and (\ref{complex duality regularization2}) to (\ref{complex lagrange duality1}), the final form of Lagrange duality can be obtained
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize\quad \theta=-\frac{1}{2}[\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}+\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}]\\
\nonumber
-\sum_{i}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta+\hat{\beta}_{i})\epsilon+[\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})]\\
\nonumber
+C\sum_{i}^{N_{r}}(\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i}))\\ 
\left\{\begin{array}{ll}
0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
\xi^{r}(\hat{\xi}^{r})\geq 0\\
\xi^{i}(\hat{\xi}^{i})\geq 0\\
\end{array}\right.
\label{final complex lagrange duality}
\end{IEEEeqnarray}
which can be divided into 2 independent regression task,

@@

Fig.\ref{figure3} demonstrates the relation between the number of users ($N_{t}$) and $E[\ln(\phi_{om})]_{t}$ under cases of different numbers of antennas at base station ($N_{r}$). From Fig.\ref{figure3}, we can see, on the one hand, with $N_{r}$ fixed, $E[\ln(\phi_{om})]$ decreases while $N_{t}$ increases, however the gradient of each curve becomes more and more gentle. On the other hand, when $N_{r}$ becomes larger $E[\ln(\phi_{om})]$ becomes more insensitive to variation of $N_{t}$.
\section{Stopping Criteria}\label{stopping criteria}
As we have explained in section \ref{section lagrange duality}, the upper bound of Lagrangian dual objective function is determined by primal objective function, further more the optimal of primal and dual objective function is found if and only if the equality holds, that is 
\theta(\lambda^{r}, \lambda^{i})=f(\mathbf{w},\xi)
\label{duality equal}
\frac{1}{2}||\mathbf{w}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
\label{simple primal}
(\ref{final complex lagrange duality}) can be rewritten as follow by substituting $\lambda^{r}=\alpha-\hat{\alpha}$, $|\lambda^{r}|=\alpha+\hat{\alpha}$ and $\lambda^{i}=\beta-\hat{\beta}$, $|\lambda^{i}|=\beta+\hat{\beta}$

@@

\theta(\lambda^{r}, \lambda^{i})=-\frac{1}{2}<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>-\frac{1}{2}<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>+<Re(\mathbf{y})^{T}, \lambda^{r}>+<Im(\mathbf{y})^{T}, \lambda^{i}>\\
-\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i})],
\label{simple dual function}

@@

Similarly, (\ref{complex duality regularization1}) can be formulated as 
||\mathbf{W}||^{2}_{\mathbb{H}}=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>,
\label{simple regularization}
hence, duality gap can be formulated as

@@

\label{intermediate function2}
Therefore based on (\ref{simple risk function1})-(\ref{intermediate function2}), duality gap in (\ref{simple duality gap}) can be rewritten as 
